\newpage
\appendix
\section{Survey: The Wide Role of Informatics at Universities}\label{apx:survey}
\begin{enumerate}
\item Research
\begin{enumerate}
\item When compared with single disciplinary research, does your
university encourage or discourage (or neither) interdisciplinary
research? If so how? (e.g. funding, time, physical centres)
\begin{itemize}
\item Encourage
\item Discourage
\item Neither encourage nor discourage
\end{itemize}
\item Does your Informatics department encourage or discourage (or
neither) interdisciplinary research? If so how?
\begin{itemize}
\item Encourage
\item Discourage
\item Neither encourage nor discourage
\end{itemize}
\item Are there interdisciplinary areas of research where your university
could (should) enter but aren't due to lack of university support? If so
what are they?
\item Are there other players who have helped increase the
interdisciplinary research in your university?
For example has a funding body focused a programme on
interdisciplinary PhD studentships which academics applied for?If so
what external organisations and what programmes have increased
interdisciplinary research at your university?
\item Please comment on any advantages or disadvantages you perceive
of your university's arrangements.
\end{enumerate}
\item Teaching
\begin{enumerate}
\item Does your university run joint degrees (e.g. X and Informatics, Informatics and X, X with Informatics, Informatics with X). If yes,
what are they?
\begin{itemize}
\item Yes
\item No
\end{itemize}
\item Are there plans to run new joint degrees or to close down joint
degrees? If yes what are they?
\begin{itemize}
\item Run new joint degrees
\item Close down joint degrees
\item Neither run nor close down
\end{itemize}
\item Who teaches the Informatics component of non-Informatics degrees? For example, is programming taught to Physicists by members
of the Physics department, of the Informatics department or is there a
servicing organisation within your university that teaches Physics
students to code (or some other mechanism)?
\item If Informatics is taught by people not located in an Informatics
 department are they Computer Scientists by training or research?
 \begin{itemize}
\item They are Computer Scientists
\item They are not Computer Scientists
\item Informatics is not taught by people not located in an Informatics department
\end{itemize}
\item Please comment on any advantages or disadvantages you perceive of your university?s arrangements.
\end{enumerate}
\item People
\begin{enumerate}
\item Does your university explicitly advertise/hire academics who focus
on interdisciplinary research?
\begin{itemize}
\item Yes
\item No
\end{itemize}
\item  Are they rooted in a department, have a joint appointment across
departments, or rooted in a centre?
\begin{itemize}
\item Rooted in a department
\item Have a joint appointment across departments
\item Rooted in a centre
\end{itemize}
\item How is their quality judged for both appointment and for promotion?For example are they judged according to the criteria of one
of the departments or both? Are the people who judge from a single
department or both?
\item Are there any initiatives planned to hire in interdisciplinary areas?
\begin{itemize}
\item Yes
\item No
\end{itemize}
\item Please comment on any advantages or disadvantages you perceive of your university?s arrangements.
\end{enumerate}
\item Data Science
\begin{enumerate}
\item Which department in your university is seen to own this area? Is it
Informatics, Statistics, jointly or somewhere else?
\begin{itemize}
\item Informatics Department
\item Statistics Department
\item Jointly Informatics and Statistics Department
\item Somewhere else (please specify)
\end{itemize}
\item Has the rise of this area changed the perception of Informatics
overall in your university?
\begin{itemize}
\item Yes
\item No
\end{itemize}
\item Please comment on any advantages or disadvantages you perceive of
your university?s arrangements.
\end{enumerate}
\item Structure
\begin{enumerate}
\item Does your university set up centres for interdisciplinary work? If
yes can you say which they are?
\begin{itemize}
\item Yes
\item No
\end{itemize}
\item Are they for research, translation (technology transfer),
consultancy, and/or teaching?
\begin{itemize}
\item Research
\item Translation (technology transfer)
\item Consultancy
\item Teaching
\end{itemize}
\item Are they rooted in a single department (say which one), owned by
the departments involved or independent?
\begin{itemize}
\item Rooted in a single department
\item Owned by the departments involved
\item Independent
\end{itemize}
\item Are they physically located within a department, nearby or
elsewhere on campus?
\begin{itemize}
\item Within a department
\item Nearby a department
\item Elsewhere on campus
\end{itemize}
\item How are any centres funded? Does the university provide any
money to startup or are they funded by external money? Does the
university provide longer term money?
\item Are there plans to set up more centres or to close centres? If so
what will they be?
\begin{itemize}
\item Set up more centres
\item Close centres
\item Neither set up nor close
\end{itemize}
\item What are the drivers or pressures (both internal to the department/
school/faculty/university and external to the university)
that you see on the horizon that may lead to new activity?
\item Is substantial interdisciplinary work undertaken by academics
without any institutional or department support?
\begin{itemize}
\item Without any institutional or department support
\item With an institutional or department support
\end{itemize}
\item Are there any centres for interdisciplinary work that have been set
up due to a strategic decision by the university or
department/school/faculty rather than as supporting activities of
existing faculty? If so which centres?
\item Does your university have something in their official strategy to
widen the role of Informatics or to encourage interdisciplinary
research? If so what is it?
\item Please comment on any advantages or disadvantages you perceive of your university?s arrangements.
\item Is there anything we have missed in the survey that you wish to tell us?
\end{enumerate}
\end{enumerate}
\newpage
\section{The participants}\label{apx:names}
{\tiny{
\begin{table}[h]
\begin{center}
\begin{tabular}  {|r|l|l|}
\hline
&{\bf Country} & {\bf University}\\
\hline
1.&Austria   &  TU Wien\\
\hline
2.&Belgium   & Universit\' e Catholique de Louvain \\
\hline
3.&Bulgaria  &  Sofia University St. Kliment Ohridski\\
\hline
4.&Czech Republic & Masaryk University\\
\hline
5.&Denmark  &  Aalborg University\\
& &  IT University of Copenhagen \\
&  &  University of Southern Denmark\\
\hline
6.&Estonia   & Tartu University \\
\hline
7.&Finland  & Aalto University \\
\hline
8.&Germany  & RWTH Aachen \\
&  & Humboldt-Universit\H at zu Berlin \\
&  &  Paderborn University\\
&  & University of Stuttgart \\
\hline
9.&Hungary   &   E\" otv\"os Lor\'and University\\
\hline
10.&Ireland  &  Technological University Dublin\\
\hline
11.&Italy   & University of Bari Aldo Moro\\
 &  &  Universit\` a di Torino\\
 & & Alma Mater Studiorum - Università di Bologna \\
 & & *Universit\` a degli Studi di Milano \\
&  & Politecnico di Milano \\
& & Universit\` a Roma Tre \\
&  &  Universit\` a degli Studi di Milano-Bicocca\\
&  & *Universit\` a degli Studi ``G. d' Annunzio'' Chieti Pescara \\
\hline
12.&Latvia   & University of Latvia\\
&  & Transport and Telecommunication University \\
\hline
13.&Netherlands  &  Delft University of Technology\\
& & *Tilburg University \\   
& &  Utrecht University \\
 \hline
14.& Portugal  & Universidade Nova de Lisboa \\
 \hline
15.&Romania  & Babes-Bolyai Univ. Cluj-Napoca \\
\hline
16.&Spain  & *University of Almeria \\
&  & Universitat Politecnica de Catalunya \\
&  &  *University of Extremadura\\
&  &  *University Jaume I\\
&    & *University of M\' alaga \\
&  &  *Complutense University of Madrid\\
&  &  *University Oviedo\\
&  & *Universidad de Valladolid \\
\hline
17.& Sweden   &  Chalmers | Gothenburg University\\
\hline
18.&Switzerland   & University of Bern\\
& & EPFL \\
&  &  University of Lugano \\
 &    & ETH Z\" urich \\
&   &  University of Z\" urich\\
\hline
19.&UK   &  Cambridge University\\
&   &  University of Edinburgh\\
 &  & Imperial College London\\
&  & University of Oxford \\
\hline
\end{tabular}
%\vspace*{0.4cm}
\end{center}
%\caption{Participating Universities -- non IE members are marked with (*)}
\label{tab:names}
\end{table}
}}
\newpage
\section{Joint Degrees by Country}\label{apx:teaching}
\small{
\begin{table}[h]
\begin{center}
\label{tab:unis}
\begin{tabular}  {|l|l|l|}
\hline
{\bf Level}&{\bf Joint title} & {\bf Countries}\\
\hline
BSc & Economy and Computer Science & Spain, Switzerland \\
\hline
BSc & Economics and Business Informatics & Italy, Switzerland \\
\hline
BSc & Business Informatics  &  Austria, Czech, Germany \\
                                             &&Italy, Switzerland, UK, Denmark\\
\hline
BSc & Informatics and Management    & Italy,  UK \\
\hline
BSc & Informatics and Mathematics   & Netherlands, Spain, UK\\
\hline
BSc & Informatics and Statistics   & Spain\\
\hline
BSc & Informatics and Physics   & Spain, UK\\
\hline
BSc & Law and Informatics   &  Czech \\
\hline
BSc & Social sciences and Informatics   & Czech \\
\hline
BSc & Information Science /Library science   & Germany\\
\hline
BSc & Informatics Health  &Spain\\
\hline
BSc & Informatics and  Engineering   & Spain,  UK\\
\hline
BSc, MSc & Bioinformatics  & Czech, Denmark, Italy, Switzerland\\
\hline
BSc, MSc & Data Science   & Italy, Spain\\
\hline
BSc, MSc & Technical Communication    & Germany, Denmark\\
\hline
BSc, MSc & Computational Engineering   & Germany\\
\hline
MSc & ICT and Media   & Italy\\
\hline
MSc & Data Science and Entrepreneurship   & Netherlands\\
\hline
MSc & Data Science and Society   & Netherlands\\
\hline
MSc & Cognitive Science and Art. Intellig.   & Netherlands\\
\hline
MSc & Geoinformatics   & Italy\\
\hline
MSc & Data mining with political Sc.  &  Italy\\
\hline
MSc&  Informatics and Psychology   &  Italy\\
\hline
MSc & Cybernetics  &  Germany\\
\hline
MSc & Mechatronics   & Germany\\
\hline
MSc & INFOTech   & Germany\\
\hline
MSc & Comput. Sc. and Engineering & Switzerland\\
\hline
MSc& Bioinformatics  & Switzerland\\
\hline
MSc & Design Informatics    & UK, Denmark\\
\hline
\end{tabular}
%\vspace*{.4cm}
\end{center}
%\caption{Joint degrees (BSc and MSc) and countries}
\label{ tab:joint}
\end{table}
}
