\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{The Wide Role of Informatics at Universities}
\author{The Author}
%\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle
\section{Introduction}

In the 1970s with the advent of the personal computer we entered into the Digital or Information Age. However it has only been in this century with the ubiquity of the internet, the smartphone, and the internet of things that digital has become truly pervasive. How do universities respond to this massive change? Informatics Europe established in 2018 a new working group to investigate what universities are doing to ensure that non-informatics teaching and research is informed by best practice in Informatics.

To better understand the state of affairs on this topic and discover best practices at European Universities, the working group conducted an online survey. We invited heads and members of Informatics/Computer Science/IT Departments (Schools, Faculties, Institutes) to complete a questionnaire. The request to fill out our survey was sent to all Informatics Europe members and it was also publicly available from the Informatics Europe website. The questionnaire was filled out autumn 2018. Forty eight universities (almost all IE members) from eighteen countries filled it out. The list of participants is in table~\ref{tab:unis}.

Our survey was wide ranging. We wanted to understand how universities valued interdisciplinary research, about teaching Informatics to non-specialist students, what happens i n practice with hiring and supporting interdisciplinary academics. We wanted to know about how Data Science in particular fits into universities and finally the structures in place to support interdisciplinary work. The survey questions are in Appendix~\ref{appendix}. 

How Informatics (also called Computer Science or Computing) should position itself in a university is a political decision. The extremes we could imagine range from primarily being a service department to primarily being a research area that is isolated from other departments.


\begin{table}
\begin{center}
\label{tab:unis}
\begin{tabular}  {|r|l|l|}
\hline
&{\bf Country} & {\bf University}\\
\hline
1.&Austria   &  TU Wien\\
\hline
2.&Belgium   & Universit\' e Catholique de Louvain \\
\hline
3.&Bulgaria  &  Sofia University St. Kliment Ohridski\\
\hline
4.&Czech Republic & Masaryk University\\
\hline
5.&Denmark  &  Aalborg University\\
& &  IT University of Copenhagen \\
&  &  University of Southern Denmark\\
\hline
6.&Estonia   & Tartu University \\
\hline
&Finland  & Aalto University \\
\hline
7.&Germany  & RWTH Aachen \\
&  & Humboldt-Universit\H at zu Berlin \\
&  &  Paderborn University\\
&  & University of Stuttgart \\
\hline
8.&Hungary   &   E\" otv\"os Loránd University\\
\hline
9.&Ireland  &  Technological University Dublin\\
\hline
10.&Italy   & University of Bari Aldo Moro\\
 &  &  Universit\` a di Torino\\
 & & Alma Mater Studiorum - Università di Bologna \\
 & & Universit\` a degli Studi di Milano \\
&  & Politecnico di Milano \\
& & Universit\` a Roma Tre \\
&  &  Universit\` a degli Studi di Milano-Bicocca\\
&  & Universit\` a degli studi ``G. d' Annunzio'' Chieti Pescara \\
\hline
11.&Latvia   & University of Latvia\\
&  & Transport and Telecommunication University \\
\hline
12.&Netherlands  &  Delft University of Technology\\
& & Tilburg University \\   
& &  Utrecht University \\
 \hline
13.& Portugal  & Universidade Nova de Lisboa \\
 \hline
14.&Romania  & Babes-Bolyai Univ. Cluj-Napoca \\
\hline
15.&Spain  & University of Almeria \\
&  & Universitat Politecnica de Catalunya \\
&  &  University of Extremadura\\
&  &  University Jaume I\\
&    & University of M\' alaga \\
&  &  Complutense University of Madrid\\
&  &  University Oviedo\\
&  & Universidad de Valladolid \\
\hline
16.& Sweden   &  Chalmers | Gothenburg University\\
\hline
17.&Switzerland   & University of Bern\\
& & EPFL \\
&  &  University of Lugano \\
 &    & ETH Z\" urich \\
&   &  University of Z\" urich\\
\hline
18.&UK   &  Cambridge University\\
&   &  University of Edinburgh\\
 &  & Imperial College London\\
&  & University of Oxford \\
\hline
\end{tabular}
\caption{Participating Universities}
\end{center}
\end{table}



















%\subsection{}

\input{research}
\input{teaching}
\input{people}
\input{data}
\input{structure}
\input{appendix.tex}

\end{document}  
